\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-09 smurf_paper.tex
update dimm flowchart... using open office now instead of xfig

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{dimm.pdf}
\caption{Typical map-making algorithm. Raw data (stored in multiple
  files) are read and concatenated into continuous time-series. A
  pre-processing stage repairs DC steps, applies a flatfield
  correction, and identifies and removes the noisiest bolometers. The
  iterative portion then begins: estimating and removing the
  common-mode signal; applying the extinction correction; high-pass
  filtering to remove residual independent low-frequency noise;
  estimating the map by re-gridding the data; and finally measuring
  the noise in the residual time-series. If the solution has
  converged, the map is written to disk. Otherwise any multiplicative
  factors that may have been applied to the data are inverted (e.g.,
  extinction correction), and then each additive component is
  re-estimated in turn, with the previous estimate first being added
  back into the time-series (and importantly, not the other
  components).}
\label{fig:dimm}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{dimm.pdf}
\caption{Typical map-making algorithm. Raw data (stored in multiple
  files) are read and concatenated into continuous time-series, and
  flatfieded. Based on the scan speed of the telescope, the data are
  down-sampled to match the selected output map pixel size (usually 2
  and 4\,arcsec at 450 and 850\,\micron, respectively, to ensure
  adequate sampling of the \scuba\ PSFs). A cleaning stage repairs DC
  steps and spikes, and fills gaps to ensure continuity. Finally, the
  mean of each bolometer time-series is removed (higher-order
  polynomials may also be used). The iterative portion then begins
  (dashed box): estimating and removing the common-mode signal (the
  combined \model{COM} and \model{GAI} models); applying the
  extinction correction (\model{EXT}); high-pass filtering to remove
  residual independent low-frequency noise (\model{FLT}); estimating
  the map by re-gridding the data, and then removing its projection
  from the time-series (\model{AST}); and finally measuring the noise
  in the residual time-series (\model{NOI}). If the solution has
  converged, the map is written to disk. Otherwise any multiplicative
  factors that may have been applied to the data are inverted (i.e.,
  the extinction correction, \model{EXT}), and then the models for the
  low-frequency noise; the common-mode (\model{COM,GAI}) and high-pass
  filter (\model{FLT}). Each model is then re-estimated in turn until
  \model{AST}, at which point the previous estimate of the
  astronomical signal is added back into the data prior to its
  re-calculation.}
\label{fig:dimm}
\end{figure}
